Security of deployed Android devices

### 2014-01-13 netos2014-01-14.tex
Make netos talk make better use of slide area and have correct titles

\date[2013-11-13] % (optional)
{Mobile Security Reading Group WIP presentation}

\subject{Mobile Security Reading Group WIP presentation}
% This is only inserted into the PDF information catalog. Can be left
% out.

@@

\begin{frame}{Device Analyzer collects lots of data}{}
 \begin{itemize}
  \note{}
  \item Android app installed on user devices
  \item Collects data with consent and sends it to our server
  \item Built by Daniel Wagner
  \note{\\}
  \item Deployed since May 2011
  \note{\\}
  \item 70 billion records, 2000 years, 16000 devices
  \item \url{http://deviceanalyzer.cl.cam.ac.uk/}
 \end{itemize}
 \pgfdeclareimage[height=90px]{dalogo}{figures/dalogo512}
 \begin{center}
  \pgfuseimage{dalogo}
 \end{center}
\end{frame}

@@

\begin{frame}{Root equivalent vulnerabilities on Android}{}
\small \url{https://wiki.dtg.cl.cam.ac.uk/drt24/dasecurityupdates}\\
Vulnerabilities affecting all of Android (not manufacturer specific):
 \begin{itemize}
  \item exploid
  \item RageAgainstTheCage zygote
  \item RageAgainstTheCage adb setuid exhaustion
  \item KillingInTheNameOf psneuter ashmem
  \item zergRush
  \item levitator
  \item Gingerbreak
  \item APK signature verification - duplicate file entries
  \item APK signature verification - unsigned shorts
 \end{itemize}
There are also lots of manufacture/device specific vulnerabilities.
\end{frame}

 \pgfdeclareimage[height=0.9\textheight]{da_norm_api}{figures/da_norm_api}
 \pgfdeclareimage[height=0.9\textheight]{play_norm_api}{figures/play_norm_api}
\begin{frame}{Old versions of Android still in use -- Google Play API}{}
 \begin{center}
  \pgfuseimage{play_norm_api}
 \end{center}
\end{frame}

\begin{frame}{Old versions of Android still in use -- Device Analyzer}{}
 \begin{center}
  \pgfuseimage{da_norm_api}
 \end{center}
\end{frame}

\begin{frame}{Old versions of Android still in use}{Coarse grained API information}
 \pgfdeclareimage[width=0.5\textwidth]{da_norm_api_small}{figures/da_norm_api}
 \pgfdeclareimage[width=0.5\textwidth]{play_norm_api_small}{figures/play_norm_api_trunc}
 \begin{center}
  \pgfuseimage{da_norm_api_small}
  \pgfuseimage{play_norm_api_small}
 \end{center}
Device Analyzer data is representative of the versions of Android actually in use
\end{frame}

\begin{frame}{Old versions of Android still in use}{Detailed OS version}
 \pgfdeclareimage[height=0.87\textheight]{da_norm_os}{figures/da_norm_os}
 \begin{center}
  \vspace{-0.5em}
  \pgfuseimage{da_norm_os}
 \end{center}
\end{frame}

\begin{frame}{Lots of Android devices are exposed to known root equivalent vulnerabilities}{}
 \pgfdeclareimage[height=0.87\textheight]{da_proportioninsecure}{figures/proportioninsecure}
 \begin{center}
  \vspace{-0.5em}
  \pgfuseimage{da_proportioninsecure}
 \end{center}
\end{frame}

\begin{frame}{Several vulnerabilities contribute to this insecurity}{}
 \pgfdeclareimage[height=0.95\textheight]{da_vulnerabilities}{figures/vulnerabilities}
 \begin{center}
  \vspace{-0.5em}
  \pgfuseimage{da_vulnerabilities}
 \end{center}
\end{frame}

\begin{frame}{Devices do get updated}{}
 \pgfdeclareimage[height=0.95\textheight]{da_updates_between_versions}{figures/updates_between_versions}
 \begin{center}
  \vspace{-0.5em}
  \pgfuseimage{da_updates_between_versions}
 \end{center}
\end{frame}

\begin{frame}{Devices do get security updates}{}
 \pgfdeclareimage[height=0.95\textheight]{da_w_security_updates}{figures/w_security_updates}
 \begin{center}
  \vspace{-0.5em}
  \pgfuseimage{da_w_security_updates}
 \end{center}
\end{frame}

>>>>

\date[2014-01-14] % (optional)
{NetOS talklet}

\subject{NetOS talklet}
% This is only inserted into the PDF information catalog. Can be left
% out.

@@

\begin{frame}{Device Analyzer collects lots of data}{}
 \begin{itemize}
  \note{}
  \item Android app installed on user devices
  \item Collects data with consent and sends it to our server
  \item Built by Daniel Wagner
  \note{\\}
  \item Deployed since May 2011
  \note{\\}
  \item 100 billion records, 2000 years, 17000 devices %TODO update years value
  \item \url{https://deviceanalyzer.cl.cam.ac.uk/}
 \end{itemize}
 \pgfdeclareimage[height=90px]{dalogo}{figures/dalogo512}
 \begin{center}
  \pgfuseimage{dalogo}
 \end{center}
\end{frame}

@@

\begin{frame}{Root equivalent vulnerabilities on Android}{}
\small \url{http://androidvulnerabilities.org/}

Vulnerabilities affecting all of Android (not manufacturer specific):
 \begin{itemize}
  \item exploid
  \item RageAgainstTheCage zygote
  \item RageAgainstTheCage adb setuid exhaustion
  \item KillingInTheNameOf psneuter ashmem
  \item zergRush
  \item levitator
  \item Gingerbreak
  \item APK signature verification -- duplicate file entries
  \item APK signature verification -- unsigned shorts
  \item APK signature verification -- unchecked name
 \end{itemize}
There are also lots of manufacture/device specific vulnerabilities.
\end{frame}

 \pgfdeclareimage[height=0.96\textheight]{da_norm_api}{figures/da_norm_api}
 \pgfdeclareimage[height=0.96\textheight]{play_norm_api}{figures/play_norm_api}
\begin{frame}[plain]{Old versions of Android still in use -- Google Play API}{}
 \begin{center}
  \pgfuseimage{play_norm_api}
 \end{center}
\end{frame}

\begin{frame}[plain]{Old versions of Android still in use -- Device Analyzer}{}
 \begin{center}
  \pgfuseimage{da_norm_api}
 \end{center}
\end{frame}

\begin{frame}{Old versions of Android still in use}{Coarse grained API information}
 \pgfdeclareimage[width=0.51\textwidth]{da_norm_api_small}{figures/da_norm_api}
 \pgfdeclareimage[width=0.51\textwidth]{play_norm_api_small}{figures/play_norm_api_trunc}
 \begin{center}
  \hspace{-1em}\pgfuseimage{da_norm_api_small}\hspace{-0.5em}
  \pgfuseimage{play_norm_api_small}
 \end{center}
Device Analyzer data is representative of the versions of Android actually in use
\end{frame}

\begin{frame}[plain]{Detailed OS version}{}
 \pgfdeclareimage[height=0.99\textheight]{da_norm_os}{figures/da_norm_os}
 \begin{center}
  \vspace{-0.5em}
  \pgfuseimage{da_norm_os}
 \end{center}
\end{frame}

\begin{frame}[plain]{Android devices with root equivalent vulnerabilities}{}
 \pgfdeclareimage[height=0.98\textheight]{da_proportioninsecure}{figures/proportioninsecure}
 \begin{center}
  \vspace{-0.5em}
  \pgfuseimage{da_proportioninsecure}
 \end{center}
\end{frame}

\begin{frame}[plain]{Several vulnerabilities contribute to this insecurity}{}
 \pgfdeclareimage[height=0.97\textheight]{da_vulnerabilities}{figures/vulnerabilities}
 \begin{center}
  \vspace{-0.3em}
  \pgfuseimage{da_vulnerabilities}
 \end{center}
\end{frame}

\begin{frame}[plain]{Devices do get updated}{}
 \pgfdeclareimage[height=0.98\textheight]{da_updates_between_versions}{figures/updates_between_versions}
 \begin{center}
  \vspace{-0.2em}
  \pgfuseimage{da_updates_between_versions}
 \end{center}
\end{frame}

\begin{frame}[plain]{Devices do get security updates}{}
 \pgfdeclareimage[height=0.98\textheight]{da_w_security_updates}{figures/w_security_updates}
 \begin{center}
  \vspace{-0.2em}
  \hspace{-2em}\pgfuseimage{da_w_security_updates}
 \end{center}
\end{frame}
